---
title: "Causal Inference Working Group: Electric Company Case Study"
author: "Adam Peterson"
date: "9/16/2020"
output: html_document
---


# Libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,results='hide',message=FALSE}
library(tidyverse)
library(equatiomatic)
library(rstanarm)
theme_set(theme_bw() + theme(strip.background=element_blank()))
```


# Data


```{r data,message=FALSE,warning=FALSE}
df <- read_csv("https://raw.githubusercontent.com/avehtari/ROS-Examples/master/ElectricCompany/data/electric.csv") %>% 
  mutate(treatment=factor(treatment,labels=c("Control","Treatment")),
         grade = factor(grade)) %>% select(-X1)
knitr::kable(head(df))
```

* `post_test`: Outcome variable, the post treatment reading test score
* `pre_test` : Possible covariate, test taken prior to treatment
* `grade` : Classroom's grade level
* `treatment` : Binary indicator variable where 1 denotes the classroom watched the tv show and 0 indicates they did not.
* `supp` : Whether or not the class received supplemental treatment, **NOTE**: only available for 96 classes.
* `pair_id` : Denotes which class' are in which pairs



## Checking for Imbalance, Overlap

```{r EDA, echo=FALSE,message=FALSE}
df %>% 
  group_by(grade,treatment) %>% 
  mutate(mean_ptest = mean(post_test)) %>% 
  ungroup() %>% 
  ggplot(aes(x=post_test)) + 
  geom_histogram() + 
  geom_vline(aes(xintercept=mean_ptest),color='red',linetype=2) + 
  facet_wrap(treatment~grade,ncol=4)
```

### Model Estimating Treatment-Grade Main and Interaction Effects


```{r model_one_eq,echo=F,results='asis'}
fit_lm <- lm(post_test ~ treatment*grade,
                data=df)
extract_eq(fit_lm,wrap=TRUE)
```

```{r model_fit_one,message=FALSE,results='hide'}
fit <- stan_glm(post_test ~ treatment*grade,
                data=df,
                prior_intercept=NULL,prior=NULL)
```



```{r fit_print}
fit
```


```{r plot_data,message=FALSE,results='hide',echo=F}
tx_effs <- as.matrix(fit,regex_pars = "Treatment")
tx_effs <- purrr::map_dfr(1:4,function(x) tibble(Grade = x,
                                                 Treatment_Effect = if(x==1) tx_effs[,1] else tx_effs[,1] + tx_effs[,x]))
tx_effs <- tx_effs %>% group_by(Grade) %>% 
  summarise(Lower= quantile(Treatment_Effect,0.025),
            lower = quantile(Treatment_Effect,0.25),
            Median = quantile(Treatment_Effect,0.5),
            upper = quantile(Treatment_Effect,0.75),
            Upper = quantile(Treatment_Effect,0.975)) %>% 
  mutate(Grade = factor(Grade))
```

```{r plot_results_one,echo=F}
tx_effs %>% 
  ggplot(aes(x=forcats::fct_rev(Grade),y=Median)) + 
  geom_pointrange(aes(ymin=Lower,ymax=Upper),linetype=2) + 
  geom_pointrange(aes(ymin=lower,ymax=upper),linetype=1) + 
  coord_flip() + xlab("Grade") + ylab("") + ggtitle("Treatment Effect") +
  geom_hline(aes(yintercept=0),linetype=3,color='red')
```



## Pre Treatment Predictors

Would including the `pre_test` covariate in the model help?

```{r pre_treatment_plot,message=FALSE,echo=F}
ggplot(aes(x=pre_test,y=post_test,color=treatment),data=df) +
  geom_point(aes(shape=treatment)) + 
  geom_smooth(method='lm',se = FALSE,) + 
  facet_wrap(~grade) + 
  scale_color_manual(values=c("black","darkgrey")) + 
  ggtitle("Grade Specific Electric Company Treatment/Control Effects on Reading Test")
```


### Model with Pre-Test Included

```{r model_two_eq,echo=F,results='asis'}
fit_lm <- lm(post_test ~ treatment*grade + pre_test*grade, 
                data=df)
extract_eq(fit_lm,wrap=TRUE) 
```

```{r pretreatment_model,message=FALSE,results='hide'}
fit <- stan_glm(post_test ~ treatment*grade + pre_test*grade,
                data=df,
                prior_intercept=NULL,prior=NULL)
```

```{r pretreat_print}
fit
```


```{r plot_data_manipulate2,echo=F,message=F}
ptx_effs <- as.matrix(fit,regex_pars = "Treatment")
ptx_effs <- purrr::map_dfr(1:4,function(x) tibble(Grade = x,
                                                 Treatment_Effect = if(x==1) ptx_effs[,1] else ptx_effs[,1] + ptx_effs[,x]))
ptx_effs <- ptx_effs %>% group_by(Grade) %>% 
  summarise(Lower= quantile(Treatment_Effect,0.025),
            lower = quantile(Treatment_Effect,0.25),
            Median = quantile(Treatment_Effect,0.5),
            upper = quantile(Treatment_Effect,0.75),
            Upper = quantile(Treatment_Effect,0.975)) %>% 
  ungroup() %>% 
  mutate(Grade = factor(Grade),
         Model = "Adjusted")
```


```{r plot_mod_results2,echo=F}
pltdf <- rbind(tx_effs %>% mutate(Model = "Unadjusted"),
               ptx_effs) %>% 
  mutate(Model = factor(Model,levels = c("Unadjusted","Adjusted")))

pltdf %>% 
  ggplot(aes(x=forcats::fct_rev(Grade),y=Median)) + 
  geom_pointrange(aes(ymin=Lower,ymax=Upper),linetype=2) + 
  geom_pointrange(aes(ymin=lower,ymax=upper),linetype=1) + 
  coord_flip() + xlab("Grade") + ylab("") + 
  geom_hline(aes(yintercept=0),linetype=3,color='red') +
  facet_wrap(~Model)
```

**NOTE** 
We could also run this analysis by stratifying by grade:  

1. How would you fit those models? 
2. How would you plot the output? 
3. Do the estimates change?
4. Does the precision in estimation change?

## Model Stratification


```{r stratified_model_fit}
## Insert code here to run stratified model fit

```


```{r strata_plot}
## Insert code here to plot new model fits

```
